\section{Introduction}
Modern solar physics, similar to astrophysics, requires increasingly complex 
software tools both for the retrieval as well as the analysis of data. The Sun 
is the most well-observed star. As such, solar physics is unique in its ability 
to access large amounts of high resolution ground- and space-based observations 
of the Sun at many different wavelengths and spatial scales with high time 
cadence. Modern solar physics, similar to astrophysics, therefore requires 
increasingly complex software tools, both for the retrieval and the analysis of 
data. For example, NASA's Solar Dynamics Observatory (SDO) satellite records 
over 1 TB of data per day all of which is telemetered to the ground and 
available for analysis. As a result, scientists have to process large volumes 
of complex data products. In order to make meaningful advances in solar 
physics, it is important for the software tools to be standardized, easy to 
use, and transparent, so that the community can build upon a common foundation.

Currently, most solar data analysis is performed with a large library of 
routines called SolarSoft, also referred to as SSW \cite{ssw_ref}. SolarSoft is a set of integrated software 
libraries, databases, and system utilities which provide a common programming 
and data analysis environment for solar physics. It is overwhelmingly an 
environment which relies upon IDL (Interactive Data Language), a commercial and 
closed-source interactive data analysis environment sold by Exelis, a global 
aerospace, defense, information and services company. The SSW gen package
provides the base analysis capabilities such as time series analysis, time 
conversions, spectral fitting, image display, and file I/O. It is composed of 
89\% IDL code while the remainder is mostly perl (5.4\%) and csh scripts 
(3.8\%). According to data generated using David A. Wheeler's 'SLOCCount', 
SSW/gen is composed of 289,724 lines of code with a total approximate value of 
\$10.4M (based on the Basic COCOMO model). Individual missions and instruments 
provide additional optional packages to support and process their data. 
For example, the SDO package \cite{sdo} is 100\% IDL code and is 11k lines of code (\$360k) 
and the SOHO package \cite{soho} is 100k lines of 
code (\$3M) and is 99.9\% IDL code. SSW is hosted and distributed by the 
Lockheed Martin Solar and Astrophysics Laboratory.

%The RHESSI package is 99.97\% IDL code and is 145k total lines of code (\$5M)

While SSW is open-source and freely available, the IDL core. The cost of IDL is prohibitive
for many undergraduates as well as institutions with limited means. 

One of SunPy's key aims is to provide a free and modern alternative 
to the SolarSoft (gen) library. This is made possible by the recent rise of the 
scientific Python community. Python is a general purpose high-level programming 
language. It is free to use, cross-platform and is both an accessible and powerful
programming language. Python is one of the top ten most popular programming languages 
in the world according to the 2014 TIOBE Index\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}.
It therefore has a very large user community which extends far outside of the solar 
physics or astronomy communities. It is very extensible with C, C++, Fortran or 
even IDL. Many books and on-line documentation is 
available. For example at the time writing a search on Amazon for books 
on IDL programming generated $189$ results while a search for Python yielded 
$1,788$ results. Python has a strong emphasis on 
readability a concept which is well-aligned with the scientific endeavor.
Additionally, Python is increasingly being taught in universities,
which means that research projects can begin quickly 
without the need for students to learn a new (and relatively niche) 
language. Finally, knowledge of Python is a skill which is useful and well 
compensated outside of the scientific community (average salary of \$110k in 
the Washington DC area according to indeed.com at the time of writing).
Python continues to see increased use in the astronomy community 
\cite{2011ASPC..442..425G} which has similar goals and requirements as the solar physics
community. Finally, Python plays well with many technologies such as web servers \cite{2008JPhCS.119d2011D}, 
SQL databases, interactive and shareable notebook-based computing \cite{PER-GRA:2007}.
For all of these reasons, Python is an ideal platform for a modern solar physics 
data analysis environment.

SunPy is built on top of the core scientific Python packages namely 
\texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib}. These core packages provide
capabilities surpassing that provided by IDL for array manipulation and 2-d plotting
\cite{2011ASPC..442..425G}. Providing similar capabilities as SSW/gen in Python is made
easier by leveraging the diverse Python community. For example, SunPy makes use of 
the \texttt{Pandas} package to provide high-performance, easy-to-use data structures and data analysis tools
for time series data\cite{mckinney2012python}. \texttt{Pandas} was originally developed for quantitative analysis of financial
data and has seen grown into a generalized data analysis package. SunPy also relies on 
and is coordinating with the \texttt{Astropy} package \cite{2013A&A...558A..33A}. It is still in
active development but already provides many relevant capabilities such as full-featured
support for FITS files, absolute dates and time conversions, units and unit conversions,
and model-fitting. Pandas (134k lines of code) and AstroPy (90k lines of code) allow
SunPy to leverage a total value of \$7.6M worth of development which is close to the 
\$10.4M for SSW/gen assuming a rough equivalency between a line of Python code and a line
of IDL code. 

The design philosophy of SunPy is to provide a clean, simple to use, and well structured package that provides 
the \textit{core} tools for solar physics. The primary focus of SunPy's 
development early development is to provide specialised, linked, datatypes 
that allow the import, processing and visualisation of all types of solar data. These include \texttt{Map}, 
\texttt{LightCurve} and \texttt{Spectrum}, these cover spatial, timeseries and spectral data  
respectively. 

The purpose of this paper is to provide an overview of SunPy's current 
capabilities, an overview of the development model and community aspects of the 
SunPy project as well as future plans. The latest release of SunPy is available 
in PyPI and can be installed in the usual manner.

%citations
% 2013A&A...558A..33A http://adsabs.harvard.edu/abs/2013A&A...558A..33A astropy
% 2011ASPC..442..425G http://adsabs.harvard.edu/abs/2011ASPC..442..425G greenfield2011
% 2013ApJ...763...86L  http://adsabs.harvard.edu/abs/2013ApJ...763...86L chianti
%@book{mckinney2012python,
%  title={Python for Data Analysis: Data Wrangling with Pandas, NumPy, and IPython},
%  author={McKinney, W.},
%  isbn={9781449323615},
%  url={http://books.google.com/books?id=v3n4\_AK8vu0C},
%  year={2012},
%  publisher={O'Reilly Media}
%}
% 2008JPhCS.119d2011D http://adsabs.harvard.edu/abs/2008JPhCS.119d2011D rapid web development in python
%@Article{PER-GRA:2007,
%  Author    = {P\'erez, Fernando and Granger, Brian E.},
%  Title     = {{IP}ython: a System for Interactive Scientific Computing},
%  Journal   = {Computing in Science and Engineering},
%  Volume    = {9},
%  Number    = {3},
%  Pages     = {21--29},
%  month     = may,
%  year      = 2007,
%  url       = "http://ipython.org",
%  ISSN      = "1521-9615",
%  doi       = {10.1109/MCSE.2007.53},
%  publisher = {IEEE Computer Society},
%}

