\section{Core Data Types}
One of the primary focus' of the SunPy library is to provide data structures 
that are specifically designed for the various types of data generally 
processed for solar physics. Currently SunPy provides three data 
types, each separate from one another to process 2D spatial data 
(\texttt{Map}), 1D temporal series (\texttt{LightCurve}) and 1 and 2D spectra 
(\texttt{Spectrum} and \texttt{Spectra}).

The design of SunPy's core data types is as a wrapper around a data object, 
either a \texttt{numpy} \texttt{ndarray} or a \texttt{pandas} 
\texttt{DataFrame}, for \texttt{Map} and \texttt{Spectra} and 
\texttt{LightCurve} respectively. Each data type has a \texttt{.data} attribute 
where this data object is located and some meta data. It is possible to 
instantiate the data types from various different sources, \textit{e.g.} files, 
urls, arrays or time ranges. The specific sources supported is dependant upon 
which data type and which instrument. All the SunPy data types support 
specialisation on a per-instrument basis, \textit{i.e.} \texttt{Map} has a 
\texttt{AIAMap} sub-type. This design allows simple extensions to cope with the 
diversity of data from different sources in solar physics. As well as support 
for different instruments and data sources each data type supports different 
visualisation wrappers that allow both quick view plotting (the peek command) 
and more fine-grained control plotting that integrates well with 
\texttt{matplotlib} (the plot command).

This section will give a brief overview of the \textit{current} functionality 
of each of these modules.

\input{2-1-Map}
\input{2-2-Lightcurve}
\input{2-3-Spectra}

\subsection{Visualisation}
\label{subsec:Viz}
As has been demonstrated in this section, the core SunPy datatypes include 
visualisation code that is specialised to that data type. These visualisation 
methods all currently utilise the matplotlib package, and are designed in such 
a way that they integrate well with the pyplot functional interface of 
matplotlib, as demonstrated in Listing \ref{code:mpl_1}.

\begin{listing}[h]
\begin{minipage}{0.49\columnwidth}
\begin{minted}{python}
import sunpy.map
import matplotlib.pyplot as plt

#Read in a aia file using SunPy
aiamap = sunpy.map.Map('aia.fits')

#Create the figure and axis 
#explicitly
fig = plt.figure()
ax = plt.subplot()

#Create a image plot with raw data
im = ax.imshow(aiamap.data,...)
#add a colour bar
plt.colorbar(im,ax=ax)

#Add a title
plt.title("My AIA plot")
plt.show()
\end{minted}
\end{minipage}
\begin{minipage}{0.49\columnwidth}
\begin{minted}{python}
import sunpy.map
import matplotlib.pyplot as plt

#Read in a aia file using SunPy
aiamap = sunpy.map.Map('aia.fits')

#Create the figure and axis 
#explicitly
fig = plt.figure()
ax = plt.subplot()

#Plot the AIA map
im = aiamap.plot(axes=ax)
#add a colour bar
plt.colorbar(im,ax=ax)

#Add a title
plt.title("My AIA plot")
plt.show()
\end{minted}
\end{minipage}
\caption{A simple example of how SunPy's plotting functions provide similar 
behaviour to matplotlib's pyplot interface.}
\label{code:mpl_1}
\end{listing}

This design philosophy makes the behaviour of SunPy's visualisation routines 
intuitive to those who already understand how matplotlib's interface is 
designed as well as allowing the use of the standard matplotlib commands to 
change the plot, \textit{e.g.} set the title. 
More technically what is done in the plotting routines is firstly, to make sure 
that the current state of the figure and axes is mantined in the same way as it 
is inside the \texttt{pyplot} functions. For \texttt{Map} this means setting 
\texttt{pyplot.sci()} or set current image, so that \texttt{plt.colorbar()} 
automatically detects the plotted \texttt{AxesImage} object. Secondly, it also 
means returning the same type of object as the \texttt{pyplot} interfaces 
function, \textit{i.e.} for \texttt{Map} it returns the \texttt{AxesImage} 
instance which is the same type of return as \texttt{pyplot.imshow}.
